The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-01-28 src/ms.tex
Implement suggestions by Axel
Co-authored-by: Axel Donath <axel.donath@mpi-hd.mpg.de>

The Cherenkov Telescope (CTA) will be the next generation very-high-energy
gamma-ray observatory.
It will improve over the current generation of imaging atmospheric Cherenkov telescopes (IACTs)
by a factor of five to ten in sensitivity and it will be able to observe the whole sky from a combination of two sites:
a northern site in La Palma, Spain, and a southern one in Paranal, Chile.
CTA will be able to observe gamma rays in the energy range between $20\,\mathrm{GeV}$ and $300\,\mathrm{GeV}$
using three different types of telescopes, in total over 100 telescopes are planned at the two sites.
CTA will also be the first open gamma-ray observatory.

The data analysis pipeline is developed as open source software and essentially split in two domains:
\begin{enumerate}
  \item In the low-level analysis, the properties of the recorded air shower events
    have to be estimated from the raw data.
    The raw data consists of very short (\textasciitilde $40\,\mathrm{ns}$) videos recorded with the fast and
    sensitive cameras of the telescopes.
    This includes the energy, particle type and direction of origin of the particle that induced the air shower
    and the time the shower was recorded.
  \item In the higher-level analysis, these reconstructed event lists are used together with the
    characterization of the measurement process and the low-level analysis to perform the actual scientific analysis.
    This includes energy spectra, light curves, sky maps and many more.
\end{enumerate}

@@

The high-level analysis will be based on the Gammapy~\cite{gammapy} library, which
will be the core of the CTA science tools.

@@

Together with Gammapy maintainer A.~Donath and former maintainer C.~Deil,
a total of 107 merged pull requests were contributed to ctapipe.

>>>>

The Cherenkov Telescope (CTA) will be the next generation very-high-energy
gamma-ray observatory.
It will improve over the current generation of imaging atmospheric Cherenkov telescopes (IACTs)
by a factor of five to ten in sensitivity and it will be able to observe the whole sky from a combination of two sites:
a northern site in La Palma, Spain, and a southern one in Paranal, Chile.
CTA will be able to observe gamma rays in the energy range between $20\,\mathrm{GeV}$ and $300\,\mathrm{TeV}$
using three different types of telescopes, in total over 100 telescopes are planned at the two sites.
CTA will also be the first open gamma-ray observatory.

The data analysis pipeline is developed as open source software and essentially split in two domains:
\begin{enumerate}
  \item In the low-level analysis, the properties of the recorded air shower events
    have to be estimated from the raw data.
    The raw data consists of very short (\textasciitilde $40\,\mathrm{ns}$) videos recorded with the fast and
    sensitive cameras of the telescopes.
    This includes the energy, particle type and direction of origin of the particle that induced the air shower
    and the time the shower was recorded.
  \item In the higher-level analysis, these reconstructed event lists are used together with some
    characterization of the instrument response to perform the actual scientific analysis.
    This software will be delivered as CTA science tools to the future users of the observatory.
\end{enumerate}

@@

The high level analysis (or CTA science tools) will be based on the Astropy affiliated package
Gammapy~\cite{gammapy}.

@@

Together with Gammapy maintainer A.~Donath and former maintainer C.~Deil,
a total of 107 merged pull requests were contributed to astropy.
